\documentclass{article}
\usepackage[utf8]{inputenc}

\title{Scoping Exercise II: Computational Analysis}
\author{ Ellen Kirkpatrick }
\date{August 2019}

\begin{document}

\maketitle

\section{Research Area}
Great inequality exists in health and welfare outcomes across different population groups in Australia including Indigenous Australians and culturally and linguistically diverse (CALD) groups, despite the institutionalisation of a welfare system. To what extent does the welfare system have its roots in the exclusionary and post-colonial social policies of the early 20th century and has this led to the continual systemic marginalisation of these groups?\\

\section{Problem}
I have to read through multiple sources from different databases and identify existing connections between them based on key themes.\\ 
 \\
\textbf{Goal:} A singular program within which we can access multiple sources at once to identify relevant ideas or information and draw links between them. Cross-checks should be able to be performed to check for common citations. Sources should correspond to one another according to key terms and themes.\\ 
\\
\textbf{Decomposition:}
\begin{itemize}
    \item Identify key themes or terms for information required.
    \item Use key words to search on the internet for sources. 
    \item Read abstracts. 
    \item Download relevant sources. 
    \item Open up sources and search for key terms.
    \item Read through source to decide degree of relevance.
    \item Label according to relevance (e.g. necessary, not useful etc.)
    \item Store sources according to key themes, issues or relevance.
    \item Begin reading and analysing content of sources.
    \item Check references of most relevant sources and cross-check with other sources. 
    \item Identify main arguments of source.
    \item Begin to compile notes for further use. \end{itemize} 
\\
\textbf{Algorithm Design:}
\begin{itemize}
    \item Search government databases. Find relevant reports and data.
    \item Download relevant reports.
    \item Find key terms in abstracts and introduction.
    \item Save file in a folder according to relevance.
    \item Read sources according to key terms.
    \item Create hyperlink between related sources to link key themes, ideas and arguments. 
    \item Cross-check for common sources and references cited. 
    \item Compile relevant information. \end{itemize}



\end{document}
